Dynamic Modeling for Optimal Cryptoeconomic Policies

### 2024-01-04 Paper/main.tex
update data sources

\section{Literature Review}
\label{sec:literature}
% TODO: add new William Cong paper
My research is related to the emerging literature on modeling cryptocurrencies and the blockchain economy. Following \citet{yermack2015bitcoin} that argued that Bitcoin is not a currency, there was an interest in studying Bitcoin as a financial asset. \citet{athey2016bitcoin, garratt2018bitcoin, biais2023equilibrium, pagnotta2022decentralizing} studied equilibria in asset pricing models for Bitcoin. \citet{schilling2019some, schilling2019currency} focused on the interactions between Bitcoin and the real economy, including dollar exchange rate and currency substitution. A broader set of models for Bitcoin include \citet{bolt2020value, catalini2020some, hinzen2022bitcoin, chiu2017economics, huberman2021monopoly}. For Proof-of-Stake protocols, \citet{saleh2019volatility, saleh2021blockchain} modeled their general volatility and welfare, while \citet{catalini2020markets} examined their tokenomics in the presence of an attack. A common result of the aforementioned asset pricing models is that static token supply causes all shocks are absorbed by the token price, which explains the high volatility of Bitcoin. This provides the motivation for an endogenous token supply in my model, which adds response mechanisms in terms of dynamic policy rules therefore can potentially mitigate the price effect of exogenous shocks.

Another set of literature has attempted to identify optimal policy rules for special types of tokens. \citet{cong2021tokenomics, cong2022token} built an asset pricing model featuring token issuance as means of platform financing and user growth leveraging network effects. \citet{sockin2023decentralization, sockin2023model} modeled cryptocurrencies as platform utility tokens and discussed elastic token issuance. \citet{d2022can} studied how stablecoin issuers can profit from seigniorage while maintaining the stablecoin's peg. \citet{fernandez2021central, zhu2019framework} are examples of papers proposing optimal monetary policies for CBDCs. While the policy goals of utility tokens are very specific (defending peg for stablecoins/CBDCs, making profit for stablecoins/platform tokens), I adopt the general policy goal of maximizing user welfare, measured by consumption and transactional benefits.

My research is also related to the large literature on cryptocurrencies. Notable empirical researches include \cite{liu2021risks} on the risk factors of cryptocurrencies, \cite{makarov2020trading} on the arbitrage spreads among different cryptocurrency markets. \cite{griffin2020bitcoin} studied the relationship between Tether purchases and cryptocurrency prices. Studies on the microeconomics of blockchain mechanisms include \citet{budish2018economic, biais2019blockchain, gans2019more, gans2022mechanism, huberman2021monopoly}.

@@

\noindent Define new variables as follows:\\
$L_t$: amount of staked tokens \\
$\delta_t$: staking yield (set by protocol)\\
$\varphi_t^b$: base fee (set by protocol)\\
$\varphi_t^v$: variable fee (competitively determined by validators and users)\\

@@

The solution to this problem, and a general equilibrium solution for the extended model, are currently work in progress.

@@

Ether is the native token of the Ethereum protocol, which was originally founded in 2014 by Vitalik Buterin as a Proof-of-Work blockchain. In August 2021, the Ethereum blockchain implemented an upgrade referred to as Ethereum Improvement Proposal \#1559 or EIP-1559. EIP-1559 introduced a two-part transaction fee mechanism with an instantly-burned ``base fee" for their transactions to be included in the next block, and a ``priority fee" to pay validators for faster inclusion. In September 2022, Ethereum migrated from a Proof-of-Work (PoW) to Proof-of-Stake (PoS) consensus model (commonly known as ``the Merge"), mandating validator staking as the only source of new ETH tokens. Staking and burning together controls the supply of ETH on the blockchain.

@@

\subsection{Transaction fees}
By design of the Ethereum blockchain, information on all historical transactions are publicly visible onchain. For each transaction, I retrieved its value and the associated base fee and priority fee through onchain data provider Dune Analytics\footnote{\url{https://dune.com/}}. Daily transaction volumes are computed by summing the value of all transactions in that day. Daily base fees and priority fees are computed by summing $BaseFee_i=GasUsed_i*BaseFeePerGas_j$ and $PriorityFee_i=GasUsed_i*PriorityFeePerGas_i$, respectively over each transaction $i$ in block $j$ produced in the day. Daily fee rates are then converted into percentages of the daily transaction volume.

@@

>>>>

\subfile{literature}

@@

\noindent Define new variables as follows:\\
$L_t$: amount of staked tokens \\
$\delta_t$: staking yield (set by protocol)\\
$\varphi_t^b$: base fee (set by protocol)\\
$\varphi_t^v$: variable fee (exogenously determined by the market for block spaces)\\

@@

In the Appendix, I outline the solution to a deterministic version of the model.

@@

Ether is the native token of the Ethereum protocol, which was originally founded in 2014 by Vitalik Buterin as a proof-of-work blockchain. In August 2021, the Ethereum blockchain implemented an upgrade referred to as Ethereum Improvement Proposal \#1559 or EIP-1559. EIP-1559 introduced a two-part transaction fee mechanism with an instantly-burned ``base fee" for their transactions to be included in the next block, and a ``priority fee" to pay validators for faster inclusion. In September 2022, Ethereum migrated from a proof-of-work (PoW) to proof-of-stake (PoS) consensus model (commonly known as ``the Merge"), mandating validator staking as the only source of new ETH tokens. Staking and burning together controls the supply of ETH on the blockchain.

@@

\subsection{Transaction fees}
By design of the Ethereum blockchain, information on all historical transactions are publicly visible onchain. For each transaction, I retrieved its value and the associated base fee and priority fee through onchain data provider Etherscan\footnote{\url{https://etherscan.io/}}. Daily transaction volumes are computed by summing the value of all transactions in that day. Daily base fees and priority fees are computed by summing $BaseFee_i=GasUsed_i*BaseFeePerGas_j$ and $PriorityFee_i=GasUsed_i*PriorityFeePerGas_i$, respectively over each transaction $i$ in block $j$ produced in the day. Daily fee rates are then converted into percentages of the daily transaction volume.

@@

\section{Calibration}
This is work in progress.
